\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

I would like to thank the following people for their help, since without them this project would not
have been possible. Thanks to them I was able to life this amazing experience.

\begin{itemize}
	\item \textbf{My mum, Arantza}, for dedicating her last days of her life to support me when I
	was starting my first months of my degree, and for being the best mother any kid could dream of.

	\item \textbf{My dad, Manu}, for being patient with me all these years and giving me the
	opportunity to continue my studies by giving me moral and financial support.

	\item \textbf{Javier García Zubía}, for being the tutor of this project and for giving me the
	opportunity to learn while working in WebLab-Deusto for the last two years.

	\item \textbf{Helena Matute}, for giving me the opportunity to work in collaboration with the
	Labpsico team and create an awesome experience.

	\item \textbf{Tomás de la Vega}, for being so receptive with my inquiries when integrating the
	Labpsico experiment.

	\item \textbf{Pablo Garaizar \emph{``Txipi''}}, for recommending me to Javier García Zubía as a
	potential candidate to work in WebLab-Deusto.

	\item \textbf{Pablo Orduña}, for letting me understand \emph{his} WebLab-Deusto and helping me
	each time I had issues in my development.

	\item \textbf{Luis Rodríguez}, for being incredibly patient with all my questions, that were not
	few.

	\item \textbf{Gabriel Martinez}, for having him in WebLab-Deusto and for being a good co-worker.
	His contributions to the \acrshort{ai} of the robot were priceless.

	\item \textbf{Ignacio Angulo}, for helping me with the electronics of the robot. I was able to
	learn a lot with him.
\end{itemize}

\chapter*{Agradecimientos}
\addcontentsline{toc}{chapter}{Agradecimientos}

Me gustaría agradecer a las siguientes personas por su ayuda, ya que sin ellas este proyecto no
habría sido posible. Gracias a ellos pude vivir esta asombrosa experiencia.

\begin{itemize}
	\item \textbf{Mi madre, Arantza}, por dedicar sus últimos días de su vida a apoyarme cuando
	comenzaba mis primeros meses de carrera, y por ser la mejor madre que ningún niño podría soñar.

	\item \textbf{Mi padre, Manu}, por ser paciente conmigo todos estos años y haberme dado la
	oportunidad de continuar mis estudios dándome a su apoyo moral y financiero.

	\item \textbf{Javier García Zubía}, por ser el tutor de este proyecto y por darme la oportunidad
	de aprender mientras trabajaba en WebLab-Deusto los últimos dos años.

	\item \textbf{Helena Matute}, por darme la oportunidad de trabajar en colaboración con el equipo
	de Labpsico y crear una experiencia sorprendente.

	\item \textbf{Tomás de la Vega}, por ser tan receptivo con mis consultas al integrar el
	experimento de Labpsico.

	\item \textbf{Pablo Garaizar \emph{``Txipi''}}, por recomendarme a Javier García Zubía como un
	candidato potencial para trabajar en WebLab-Deusto.

	\item \textbf{Pablo Orduña}, por permitirme entender \emph{su} WebLab-Deusto y ayudarme cada
	vez que tenía problemas con el desarrollo.

	\item \textbf{Luis Rodríguez}, por ser increíblemente paciente con todas mis preguntas, que no
	fueron pocas.

	\item \textbf{Gabriel Martinez}, por tenerlo en WebLab-Deusto y ser un buen compañero de
	trabajo. Sus contribuciones a la \acrshort{ia} del robot fueron impagables.

	\item \textbf{Ignacio Angulo}, por ayudarme con la electrónica del robot. Con el pude aprender
	mucho.
\end{itemize}
